Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model

### 2019-09-17 Manuscript for submission/manuscript.tex
Update

\documentclass[AMS,STIX1COL]{WileyNJD-v2}
%\documentclass[AMS]{WileyNJD-v2}
\usepackage{graphicx,times,verbatim,amsmath,amsthm}
%\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{float}  % For fixing the image in draft
\usepackage{lscape}
\usepackage[nottoc,notlot,notlof]{tocbibind}

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{condition}[theorem]{Condition}
%\newtheorem{assumption}[theorem]{Assumption}
%\newtheorem{property}[theorem]{Property}
%\newtheorem{result}[theorem]{Result}
%\newtheorem{example}[theorem]{Example}

@@

\begin{equation}
\label{eq:logistic01}
\mathbb{P}(X_{ij}=1) = \frac{e^{\alpha + f_i^T D f_j }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\alpha \in \mathbb{R}$ is a parameter and matrix $D \in \mathbb{R}^{K \times K}$ is a diagonal matrix: $D = \mbox{diag}\{d_{1},d_{2},\ldots,d_{K}\}$.
We assume $d_{ii} > 0$ for $1 \le i \le K$.
Another way to put \eqref{eq:logistic01} is
\begin{equation}
\label{eq:logistic02}
\mathbb{P}(X_{ij}=1) = \frac{\exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}}{1 + \exp\left\{\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right\}}.
\end{equation}
A justification of the above model is that when both node $i$ and node $j$ are related to topic $k$, they have a higher chance to cite one way or the other.
We have assumed a common strengthen coefficient $d_k$ ($1\le k \le K$) for factor $k$, despite different nodes.
We denote a matrix $F = \{f_1, f_2, \ldots, f_n\} \in \mathbb{R}^{K \times n}$.
Each column $i$ in matrix $F$ contains the factor loadings associated with the node $i$ ($1\le i \le n$).
Given the diagonal matrix $D$ and the factor loading matrix $F$, we assume that $X_{ij}$'s are independent; therefore we have the total conditional probability function as follows:
\begin{equation}
\label{eq:logistic03}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \prod_{1\le i<j \le n} \mathbb{P}(X_{ij})
= \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha + f_i^T D f_j) }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\mathbb{P}(X_{ij})$ is given in \eqref{eq:logistic02}.
The last equation holds because $X_{ij}$ only takes binary (i.e., $0$ or $1$) values.
Recall that the dot product of two matrices with same dimensionality, $A,B\in \mathbb{R}^{a \times b}$, is defined as $A\bullet B=\mbox{trace}(A^T B) = \sum_{i=1}^a\sum_{j=1}^b a_{ij}b_{ij}$.
The above \eqref{eq:logistic03} can be further rewritten as
\begin{equation}
\label{eq:logistic04}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where we assume $X_{ii}=0$ for all $i$ ($1\le i \le n$) and $X_{ij} = X_{ji}$ for all $i$ and $j$ ($1\le i,j \le n$), i.e., the matrix $X$ is symmetric.
The above delivers a factor analysis model.
Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g.,\cite{joreskog1969general, mcdonald2014factor,lord2008statistical, rasch1980probabilistic, harman1960modern, joreskog1970general}).

Our work is motivated from a recent work {\emph{Fused Latent and Graphical (FLaG) model} (Chen et al, 2016, \cite{chen2016fused}).
They assume that majority of variation of responses can be accounted by low dimensional latent vector, and remaining dependent structure of responses can be explained by sparse graphical structure.
Thus, the resulting model contains a low-dimensional latent vector and a sparse conditional graph.
Their key idea is to separate these two dependent structures so that they can facilitate the statistical inference.
In our model, we also assume that there exist two dependent structures among citation edges in a network.
A low-dimensional version of the aforementioned latent vector model is largely correct and majority of the citations among the nodes are induced by these common latent vectors $f_{i}$'s (with weight coefficients $d_{i}$'s).
There is still a small remainder due to the sparse graphical component.

@@

\item In FLaG model, a collection of binary responses for each question in the questionnaire follows a joint distribution, which is a combination of the Item Response Theory (IRT) model and the Ising model.
    We model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of the Latent Factor Analysis model and the sparse graphical model.

@@

The rest of the paper is organized as follows.
In Section \ref{sec:model-form}, we will give a presentation on how to build a model, which can encode both the latent dependent structure due to the common topics and the remaining sparse ad-hoc dependent structure.
In Section \ref{sec:estimate}, we will discuss the assumptions in our model and penalization on likelihood function that is constructed in Section \ref{sec:model-form}.
Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem formulated in Section \ref{sec:estimate}.
In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians.
We finally conclude this work in Section \ref{sec:Con} with several open questions and some directions for future research.

@@

Recall the following graphical model that was established in \eqref{eq:logistic04}, which is essentially a factor model (latent variable model):
$$
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \frac{\exp(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F))}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
$$
where
$X_{ij}, 1\le i,j \le n$, are binary random variables indicating either node $i$ cites node $j$ or vice versa,
matrix $X = \{X_{ij}\} \in \mathbb{R}^{n \times n}$ is symmetric with diagonal entries all being equal to zero,
factor loading matrix $F = [f_1,f_2,\ldots,f_n]\in \mathbb{R}^{K\times n}$ records the relation between nodes and the underlying topics, $F^T$ is the transpose of $F$,
and matrix $D \in \mathbb{R}^{K \times K}$  is diagonal with entries being the weight coefficients of factors.

The above specifies a latent model (or equivalently a factor model).
We now describe a graphical model as follows.
The graphical model will complement the latent model by characterizing links that are not interpretable via common factors.
For the aforementioned binary random variable $X_{ij}$, $1\le i,j \le n$, we define
\begin{equation}
\label{eq:logistic05}
\mathbb{P}(X_{ij}=1) = \frac{e^{\alpha' + S_{ij} }}{1 + e^{\alpha' + S_{ij} }},
\end{equation}
where $S_{ij} \in \mathbb{R}$, for $1\le i,j \le n$, denotes the relation between nodes $i$ and $j$.
Note that the matrix $S$ is introduced to capture the ad-hoc links in the graph.
If we have $S_{ij}\leq0$, then it is less likely to have a citational relationship between nodes $i$ and $j$.
On the other hand, if $S_{ij}>0$, then it is more likely to have a citation link between nodes $i$ and $j$.
Here parameter $\alpha' \in \mathbb{R}$ plays the same role as parameter $\alpha$ does in model \eqref{eq:logistic01}.
Denote the matrix $S = \{S_{ij}, 1\le i,j \le n \} \in \mathbb{R}^{n \times n}$.
Assume that given the matrix $S$, the binary random variables
$X_{ij}$'s are independent;
consequently, we have the total conditional probability function as follows:
\begin{eqnarray}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
&=& \prod_{1\le i<j \le n} \mathbb{P}(X_{ij}) \nonumber \\
&=& \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha' + S_{ij}) }}{1 + e^{\alpha' + S_{ij} }} \nonumber \\
&=& \frac{\exp(\alpha' \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet S)}{\prod_{1\le i<j \le n}  1 + e^{\alpha' + S_{ij} }}.
\label{eq:logistic06}
\end{eqnarray}
Recall that we have assumed that $X_{ii}=0$ for all $i$ ($1\le i \le n$) and $X_{ij} = X_{ji}$ for all $i$ and $j$ ($1\le i,j \le n$), i.e., the matrix $X$ is symmetric.
In the combined model, we integrate \eqref{eq:logistic04} and
\eqref{eq:logistic06} to render the joint conditional probability function as follows:
\begin{eqnarray}
\label{eq:logistic07}
\mathbb{P}(X \mid \alpha,  F, D, S)
&=&  \prod_{1\le i<j \le n}
\frac{e^{X_{ij}(\alpha + S_{ij} + f_i^T D f_j) }}{1 + e^{\alpha + S_{ij}+ f_i^T D f_j}} \nonumber \\
&=& \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F) +\frac{1}{2} X \bullet S\right)}{\prod_{1\le i<j \le n}  \left(1 + e^{\alpha + f_i^T D f_j +S_{ij}}\right) }.
\end{eqnarray}

@@

\item To ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that the eigen-vector of $L$ is centered, that is,
\[
    JLJ = L \quad \mbox{where} \quad
    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T,
\]
where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$s. This condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.

@@

\section{Non-asymptotic error bound of the estimator}
In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the number of papers in network is explicitly tracked. We are interested in solving the following optimization problem :
\begin{equation}\label{eq:Modified}
\min\limits_{\alpha \in R, S = S^T \atop L \succcurlyeq 0}
-\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{\exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+\exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
\end{equation}

@@

\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):
\[
\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
\]
For any vector $a$, $diag(a)$ is the diagonal matrix with elements of $a$ on its diagonal. For any square matrix $A$ and $B$, $ A \succcurlyeq B $ if and only if $A-B$ is positive semi-definite.
\end{assumption}

\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$. We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}. We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
\end{assumption}

With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through following theorem. In our result, we measure error using squared Frobenius norm summed across three matrices:
\[
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
\]

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1} and \ref{Ass:2},
if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align} \label{eq:49}
\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
\end{align}
There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
\begin{align}
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
\end{align}
where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
\end{theorem}

We would first like to note readers that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to generalized linear model.
Our work considers a logistic loss function whose parameters are characterized by sparse matrix plus low rank matrix, whereas \cite{agarwal2012noisy} works on quadratic loss of noisy realization of linear transformation of sum of low rank and sparse matrices.
We show that similar proof techniques can be applied in our case, giving us similar results.
%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.

@@

\subsection{ADMM approach}
\label{sec:ADMM}
We give a review of the alternating direction method
of multiplier (ADMM).
Consider two closed convex functions
$$
f : \chi_f \to \mathbb{R} \mbox{ and } g : \chi_g \to \mathbb{R},
$$
where the domain $\chi_f$ and $\chi_g$ of functions $f$ and $g$ are closed convex subsets of $\mathbb{R}^d$, and $\chi_f \bigcap \chi_g$ is nonempty.
Both $f$ and $g$ are possibly non-differentiable.
The alternating direction method
of multiplier is an iterative algorithm that solves the following generic optimization problem:
$$
\min_{x \in \chi_f \bigcap \chi_g} \left\{f(x) + g(x) \right\},
$$
or equivalently
\begin{eqnarray}
\label{eq:admm1}
\min_{x \in \chi_f, z\in \chi_g} & \left\{f(x) + g(z) \right\}, \\
\mbox{ subject to } & x = z. \nonumber
\end{eqnarray}
To describe the algorithm, we will need the following proximal operators
\begin{itemize}
\item $\mathbf{P}_{\lambda,f}: \mathbb{R}^d \to \chi_f$ as
$$
\mathbf{P}_{\lambda,f}(v) = \mbox{arg min}_{x \in \chi_f} \left\{
f(x) + \frac{1}{2\lambda} \|x-v\|^2_2
\right\}
$$

@@

\end{itemize}
The convergence properties of the algorithm are summarized in the following result in \cite{boyd2011distributed}.
Let $p^\ast$ be the minimal value in \eqref{eq:admm1}.

@@

\begin{itemize}
  \item Non-parametric Bayesian Statistics ($17$ papers)
  \item Functional Data analysis ($35$ papers)
  \item Dimension Reduction ($23$ papers)
  \item Mixed topics ($329$ papers)
\end{itemize}

>>>>

\documentclass[AMS,STIX1COL]{WileyNJD-v2}
%\documentclass[AMS]{WileyNJD-v2}
\usepackage{graphicx,times,verbatim,amsmath,amsthm}
%\usepackage{graphicx,times,verbatim,amsmath,amssymb,amsthm}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{float}  % For fixing the image in draft
\usepackage{lscape}
\usepackage[nottoc,notlot,notlof]{tocbibind}
\newcommand{\block}[1]{
  \underbrace{\begin{matrix}1 & \cdots & 1\end{matrix}}_{#1}
}
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{condition}[theorem]{Condition}
%\newtheorem{assumption}[theorem]{Assumption}
%\newtheorem{property}[theorem]{Property}
%\newtheorem{result}[theorem]{Result}
%\newtheorem{example}[theorem]{Example}

@@

\begin{equation}
\label{eq:logistic01}
\mathbb{P}(X_{ij}=1) = \frac{e^{\alpha + f_i^T D f_j }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\alpha \in \mathbb{R}$ is a parameter and matrix $D \in \mathbb{R}^{K \times K}$ is a diagonal matrix: $D = \mbox{diag}\{d_{1},d_{2},\ldots,d_{K}\}$.
We assume $d_{ii} > 0$ for $1 \le i \le K$.
Another way to put \eqref{eq:logistic01} is
\begin{equation}
\label{eq:logistic02}
\mathbb{P}(X_{ij}=1) = \frac{\exp\left(\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right)}{1 + \exp\left(\alpha + \sum_{k=1}^K f_{ik}f_{jk}d_{k} \right)}.
\end{equation}
A justification of the above model is that when both node $i$ and node $j$ are related to topic $k$, they have a higher chance to cite one way or the other.
We have assumed a common strengthen coefficient $d_k$ ($1\le k \le K$) for factor $k$, despite different nodes.
We denote a matrix $F = \{f_1, f_2, \ldots, f_n\} \in \mathbb{R}^{K \times n}$.
Each column $i$ in matrix $F$ contains the factor loadings associated with the node $i$ ($1\le i \le n$).
Given the diagonal matrix $D$ and the factor loading matrix $F$, we assume that $X_{ij}$'s are independent; therefore we have the total conditional probability function as follows:
\begin{equation}
\label{eq:logistic03}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \prod_{1\le i<j \le n} \mathbb{P}(X_{ij})
= \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha + f_i^T D f_j) }}{1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where $\mathbb{P}(X_{ij})$ is given in \eqref{eq:logistic02}.
The last equation holds because $X_{ij}$ only takes binary (i.e., $0$ or $1$) values.
Recall that the dot product of two matrices with same dimensionality, $A,B\in \mathbb{R}^{a \times b}$, is defined as $A\bullet B=\mbox{trace}(A^T B) = \sum_{i=1}^a\sum_{j=1}^b a_{ij}b_{ij}$.
The above \eqref{eq:logistic03} can be further rewritten as
\begin{equation}
\label{eq:logistic04}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
= \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F)\right)}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
\end{equation}
where we assume $X_{ii}=0$ for all $i$ ($1\le i \le n$) and $X_{ij} = X_{ji}$ for all $i$ and $j$ ($1\le i,j \le n$), i.e., the matrix $X$ is symmetric.
The above delivers a factor analysis model.
Various linear and nonlinear latent variable models have been studied extensively in the literature (e.g.,\cite{joreskog1969general, mcdonald2014factor,lord2008statistical, rasch1980probabilistic, harman1960modern, joreskog1970general}).

Our work is motivated from a recent work named {\emph{Fused Latent and Graphical (FLaG) model} (Chen et al, 2016, \cite{chen2016fused}).
They assume that majority of variation of responses can be accounted by low dimensional latent vector, and remaining dependent structure of responses can be explained by sparse graphical structure.
Thus, the resulting model contains a low-dimensional latent vector and a sparse conditional graph.
Their key idea is to separate these two dependent structures so that they can facilitate the statistical inference.
In our model, we also assume that there exist two dependent structures among citation edges in a network.
A low-dimensional version of the aforementioned latent vector model is largely correct and majority of the citations among the nodes are induced by these common latent vectors $f_{i}$'s (with weight coefficients $d_{i}$'s).
There is still a small remainder due to the sparse graphical component.

@@

\item In FLaG model, a collection of binary responses for each question in the questionnaire follows a joint distribution, which is a combination of the Item Response Theory (IRT) model and the Ising model.
    We model the citation edges among papers as random variables, whose dependent structure is characterized by the combination of the Latent Factor Analysis model and the Sparse Graphical model.

@@

The rest of the paper is organized as follows.
In Section \ref{sec:model-form}, we will give a presentation on how to build a model, which can encode both the latent dependent structure due to the common topics and the remaining sparse ad-hoc dependent structure.
In Section \ref{sec:estimate}, we will discuss the assumptions in our model and penalization on likelihood function that is constructed in Section \ref{sec:model-form}.
In Section \ref{sec:theorem}, we provide a non-asymptotic error bound of the estimator.
Section \ref{sec:compute} gives the detailed procedure on how to compute the estimator of the optimization problem that is formulated in Section \ref{sec:estimate}.
In Section \ref{sec:Num-anal}, we will present simple numerical experiments on synthetic data, and application of our model on real citation network of statisticians.
We finally conclude this work in Section \ref{sec:Con} with several open questions and some directions for future research.

@@

Recall the following graphical model that was established in \eqref{eq:logistic04}, which is essentially a factor model (latent variable model):
$$
\mathbb{P}\left(\{X_{ij}, 1\le i,j \le n\}\right)
= \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F)\right)}{\prod_{1\le i<j \le n}  1 + e^{\alpha + f_i^T D f_j }},
$$
where
$X_{ij}, 1\le i,j \le n$, are binary random variables indicating either node $i$ cites node $j$ or vice versa,
matrix $X = \{X_{ij}\} \in \mathbb{R}^{n \times n}$ is symmetric with diagonal entries all being equal to zero,
factor loading matrix $F = [f_1,f_2,\ldots,f_n]\in \mathbb{R}^{K\times n}$ records the relation between nodes and the underlying topics, $F^T$ is the transpose of $F$,
and matrix $D \in \mathbb{R}^{K \times K}$  is diagonal with entries being the weight coefficients of factors.

The above specifies a latent model (or equivalently a factor model).
We now describe a graphical model as follows.
The graphical model will complement the latent model by characterizing links that are not interpretable via common factors.
For the aforementioned binary random variable $X_{ij}$, $1\le i,j \le n$, we define
\begin{equation}
\label{eq:logistic05}
\mathbb{P}(X_{ij}=1) = \frac{e^{\alpha' + S_{ij} }}{1 + e^{\alpha' + S_{ij} }},
\end{equation}
where $S_{ij} \in \mathbb{R}$, for $1\le i,j \le n$, denotes the relation between nodes $i$ and $j$.
Note that the matrix $S$ is introduced to capture the ad-hoc links in the graph.
If we have $S_{ij}\leq0$, then it is less likely to have a citational relationship between nodes $i$ and $j$.
On the other hand, if $S_{ij}>0$, then it is more likely to have a citation link between nodes $i$ and $j$.
Here parameter $\alpha' \in \mathbb{R}$ plays the same role as parameter $\alpha$ does in model \eqref{eq:logistic01}.
Denote the matrix $S = \{S_{ij}, 1\le i,j \le n \} \in \mathbb{R}^{n \times n}$.
Assume that given the matrix $S$, the binary random variables
$X_{ij}$'s are independent;
consequently, we have the total conditional probability function as follows:
\begin{eqnarray}
\mathbb{P}(\{X_{ij}, 1\le i,j \le n\})
&=& \prod_{1\le i<j \le n} \mathbb{P}(X_{ij}) \nonumber \\
&=& \prod_{1\le i<j \le n}  \frac{e^{X_{ij}(\alpha' + S_{ij}) }}{1 + e^{\alpha' + S_{ij} }} \nonumber \\
&=& \frac{\exp\left(\alpha' \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet S\right)}{\prod_{1\le i<j \le n}  1 + e^{\alpha' + S_{ij} }}.
\label{eq:logistic06}
\end{eqnarray}
Recall that we have assumed that $X_{ii}=0$ for all $i$ ($1\le i \le n$) and $X_{ij} = X_{ji}$ for all $i$ and $j$ ($1\le i,j \le n$), i.e., the matrix $X$ is symmetric.
In the combined model, we integrate \eqref{eq:logistic04} and
\eqref{eq:logistic06} to render the joint conditional probability function as follows:
\begin{eqnarray}
\label{eq:logistic07}
\mathbb{P}(X \mid \alpha,  F, D, S)
&=&  \prod_{1\le i<j \le n}
\frac{e^{X_{ij}(\alpha + S_{ij} + f_i^T D f_j) }}{1 + e^{\alpha + S_{ij}+ f_i^T D f_j}} \nonumber \\
&=& \frac{\exp\left(\alpha \sum_{1\le i< j\le n}X_{ij} +\frac{1}{2} X \bullet (F^T D F) +\frac{1}{2} X \bullet S\right)}{\prod_{1\le i<j \le n}  \left(1 + e^{\alpha + f_i^T D f_j +S_{ij}}\right) }.
\end{eqnarray}

@@

\item To ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and an arbitrary matrix $L$, we assume that the eigen-vector of $L$ is centered, that is,
\[
    JLJ = L \quad \mbox{where} \quad
    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T,
\]
where $\mathbbm{1}$ denotes a $n$-dimensional vector whose entries are all $1$'s. If we have $L=F^TDF$, this condition uniquely identifies $F$ up to a common orthogonal transformation of its columns.

@@

\section{Non-asymptotic error bound of the estimator}
\label{sec:theorem}
In this section, we focus on investigating the behaviour of non-asymptotic error bound of our estimator in the context where the number of papers in a network is explicitly tracked. We are interested in solving the following optimization problem :
\begin{equation}\label{eq:Modified}
\min\limits_{\alpha \in R, S = S^T \atop L \succcurlyeq 0}
-\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{\exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+\exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
\end{equation}

@@

\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of the log-likelihood function is bounded away from zero ($\tau > 0$):
\[
\nabla^{2}h(\Theta) = \mbox{diag}\Big(\mbox{vec}\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
\]
For any vector $a$, $\mbox{diag}(a)$ is the diagonal matrix with elements of $a$ on its diagonal. For any square matrix $A$ and $B$, we have $ A \succcurlyeq B $ if and only if matrix $A-B$ is positive semi-definite.
\end{assumption}

\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$. We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}. We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
\end{assumption}

With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through the following theorem. In our result, we measure error using squared Frobenius norm summed across three matrices:
\[
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}):=\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
\]

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1} and \ref{Ass:2},
if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align} \label{eq:49}
\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
\end{align}
then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, we have the following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
\begin{align}
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}},
\end{align}
where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
\end{theorem}

We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
Our work considers a logistic loss function whose parameters are characterized by a sparse matrix plus a low rank matrix, whereas Agarwal, et al.\cite{agarwal2012noisy} work on a quadratic loss of a noisy realization of a linear transformation of sum of a low rank matrix and a sparse matrix.
We show that similar proof techniques can be applied in our case, giving us similar results.
%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.

@@

\subsection{ADMM approach}
\label{sec:ADMM}
We give a review of the alternating direction method
of multiplier (ADMM).
Consider two closed convex functions
$$
f : \chi_f \to \mathbb{R} \mbox{ and } g : \chi_g \to \mathbb{R},
$$
where the domain $\chi_f$ and $\chi_g$ of functions $f$ and $g$ are closed convex subsets of $\mathbb{R}^d$, and $\chi_f \bigcap \chi_g$ is nonempty.
Both $f$ and $g$ are possibly non-differentiable.
The alternating direction method
of multiplier is an iterative algorithm that solves the following generic optimization problem:
$$
\min_{x \in \chi_f \bigcap \chi_g} \left\{f(x) + g(x) \right\},
$$
or equivalently
\begin{eqnarray}
\label{eq:admm1}
\min_{x \in \chi_f, z\in \chi_g} & \left\{f(x) + g(z) \right\}, \\
\mbox{ subject to } & x = z. \nonumber
\end{eqnarray}
To describe the algorithm, we will need the following proximal operators
\begin{itemize}
\item $\mathbf{P}_{\lambda,f}: \mathbb{R}^d \to \chi_f$ as
$$
\mathbf{P}_{\lambda,f}(v) = \mbox{arg min}_{x \in \chi_f} \left\{
f(x) + \frac{1}{2\lambda} \|x-v\|^2_2
\right\},
$$

@@

\end{itemize}
The convergence properties of the algorithm are summarized in the following result as in \cite{boyd2011distributed}.
Let $p^\ast$ be the minimal value in \eqref{eq:admm1}.

@@

\begin{itemize}
  \item Non-parametric Bayesian Statistics, which includes $17$ papers.
  \item Functional Data analysis, which includes $35$ papers.
  \item Dimension Reduction, which includes $23$ papers.
  \item Mixed topics, which includes $329$ papers.
\end{itemize}
